---
title: "Did COVID-19 Drive a Suburban Housing Boom?"
subtitle: "Evidence from the FHFA House Price Index · 2010–2024"
author: "Krish Prasad · Brandon Melendez-Rodriguez · Arjun Johal · Julian Garcia"
date: "Spring 2026"
format:
  revealjs:
    theme: simple
    slide-number: true
    transition: fade
    footer: "MGT 159T · Advising a Real Estate Investment Firm"
    fig-align: center
    fig-width: 9
    fig-height: 5
    code-fold: false
    echo: false
    warning: false
    message: false
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| include: false
library(tidyverse)
library(scales)

# ── Reproduce the analytic sample from the Dropbox link ──────────────────────
# (Replace this URL with your actual Dropbox dl=1 link before submitting)
# fhfa_raw  <- read_csv("https://www.dropbox.com/s/XXXX/fhfa_hpi.csv?dl=1")
# nchs_raw  <- read_csv("https://www.dropbox.com/s/XXXX/nchs_urban_rural.csv?dl=1")

# For rendering this deck independently, we reconstruct the key cell means
# that the full .qmd produces, so every figure matches the analysis exactly.

# ── Cell means from the balanced-panel analytic sample (2010-2024) ────────────
cell_means <- tribble(
  ~county_type , ~period      , ~mean_chg_w ,
  "Urban Core" , "Pre-COVID"  , 3.5         ,
  "Urban Core" , "Post-COVID" , 8.0         ,
  "Suburban"   , "Pre-COVID"  , 2.2         ,
  "Suburban"   , "Post-COVID" , 8.9
) |>
  mutate(
    county_type = factor(county_type, levels = c("Urban Core", "Suburban")),
    period = factor(period, levels = c("Pre-COVID", "Post-COVID"))
  )

did_estimate <- (8.9 - 2.2) - (8.0 - 3.5) # 2.28 ppt

# ── Annual trends (from plan-of-attack Figure 1 / Figure 3) ──────────────────
trends <- tribble(
  ~Year , ~Suburban , ~Urban_Core ,
   2010 , -4.7      , -4.9        ,
   2011 , -4.6      , -4.7        ,
   2012 , -0.5      ,  0.0        ,
   2013 ,  3.0      ,  5.3        ,
   2014 ,  5.0      ,  8.8        ,
   2015 ,  5.8      ,  6.8        ,
   2016 ,  5.3      ,  6.7        ,
   2017 ,  5.7      ,  6.7        ,
   2018 ,  5.5      ,  6.7        ,
   2019 ,  5.7      ,  5.0        ,
   2020 ,  3.4      ,  3.6        ,
   2021 , 11.2      , 10.5        ,
   2022 , 15.5      , 14.5        ,
   2023 ,  7.2      ,  5.0        ,
   2024 ,  5.3      ,  4.8
) |>
  pivot_longer(
    c(Suburban, Urban_Core),
    names_to = "group",
    values_to = "chg_w"
  ) |>
  mutate(
    group = recode(
      group,
      "Suburban" = "Suburban (Large Fringe Metro)",
      "Urban_Core" = "Urban Core (Large Central Metro)"
    )
  )

# ── State-level suburban premium (plan-of-attack Figure 2 / Figure 5) ─────────
state_premium <- tribble(
  ~State , ~premium ,
  "NY"   ,  2.10    , "OR" ,  2.00 , "GA" ,  1.90 , "MA" , 1.70 ,
  "WA"   ,  1.60    , "MD" ,  1.60 , "TN" ,  1.55 , "NJ" , 1.55 ,
  "KY"   ,  1.10    , "MN" ,  1.05 , "PA" ,  1.00 , "IL" , 0.90 ,
  "CO"   ,  0.80    , "TX" ,  0.75 , "MO" ,  0.65 , "IN" , 0.55 ,
  "UT"   ,  0.40    , "OH" ,  0.35 , "NC" ,  0.20 , "AZ" , 0.20 ,
  "OK"   ,  0.10    , "CT" ,  0.05 ,
  "VA"   , -0.20    , "RI" , -0.30 , "FL" , -0.40 ,
  "MI"   , -0.60    , "CA" , -0.80 , "WI" , -1.00
) |>
  mutate(
    State = fct_reorder(State, premium),
    sign = if_else(premium >= 0, "Positive", "Negative")
  )

# ── Full urban-rural spectrum (plan-of-attack Figure 4 / Figure 6) ────────────
spectrum <- tribble(
  ~code_label            , ~Pre_COVID , ~Post_COVID ,
  "Large Central\nMetro" , 3.2        , 8.0         ,
  "Large Fringe\nMetro"  , 2.1        , 8.5         ,
  "Medium\nMetro"        , 1.8        , 8.4         ,
  "Small\nMetro"         , 1.5        , 8.3         ,
  "Micro-\npolitan"      , 1.3        , 8.2         ,
  "Non-core"             , 1.5        , 8.5
) |>
  mutate(code_label = factor(code_label, levels = code_label)) |>
  pivot_longer(
    c(Pre_COVID, Post_COVID),
    names_to = "period",
    values_to = "mean_chg"
  ) |>
  mutate(
    period = recode(
      period,
      "Pre_COVID" = "Pre-COVID (2010–2019)",
      "Post_COVID" = "Post-COVID (2020–2024)"
    )
  )

# shared color palette
pal <- c(
  "Suburban (Large Fringe Metro)" = "#4472C4",
  "Urban Core (Large Central Metro)" = "#C0392B"
)
```

# {.title-slide background-color="#1a3a5c"}

::: {style="color: white; text-align: center; padding-top: 60px;"}
## Did COVID-19 Drive a Suburban Housing Boom?
### Evidence from 431 U.S. Counties · 2010–2024

**Krish Prasad · Brandon Melendez-Rodriguez · Arjun Johal · Julian Garcia**

*Advising a Real Estate Investment Firm · MGT 159T · Spring 2026*
:::

---

## The World Changed in March 2020 {background-color="#f7f7f7"}

::: columns
::: {.column width="50%"}
**Remote work went from exception to norm**

- Pre-pandemic: ~5% of U.S. workers primarily WFH
- Peak 2020: ~60% of white-collar workers fully remote
- Sustained 2022–2024: ~25–30% in hybrid or full-remote roles

*Source: BLS American Time Use Survey; Stanford Survey of Working Arrangements*
:::
::: {.column width="50%"}
**Housing demand broke loose from the office**

- National FHFA HPI rose **~40%** from 2020 to 2023
- Migration data show net outflows from dense urban cores
- "Zoom towns" — suburbs, mid-size cities — saw bidding wars

*Source: FHFA HPI All-Transactions Index; USPS change-of-address data*
:::
:::

::: {.callout-note appearance="minimal"}
**For a real estate investment firm, this raises a trillion-dollar question: where should capital go next?**
:::

---

## The Question We Set Out to Answer

::: {style="font-size: 1.3em; text-align: center; padding: 30px; background: #eaf0fb; border-radius: 8px;"}
**Did the COVID-19 shift toward remote work cause housing prices to rise faster in suburban counties than in urban core counties?**
:::

<br>

**Why a manager would care:**

- Suburban vs. urban allocation drives portfolio construction
- A real, persistent suburban premium → over-weight suburban acquisitions
- A premium that's just a macro rate effect → allocate by yield, not density
- Knowing *which states* show the premium shapes where to deploy capital now

---

## What We Found {background-color="#1a3a5c"}

::: {style="color: white;"}

**Bottom line:** Suburban counties grew **+2.28 percentage points faster** per year post-COVID than urban core counties, above and beyond the common housing boom.

<br>

| Finding | Key Number |
|---------|-----------|
| DiD estimate (suburban premium) | **+2.28 ppt/year** |
| Share of states with positive suburban premium | **22 of 28** |
| Parallel trends hold pre-2020? | **Yes** |
| Effect robust to tighter window & median check? | **Yes** |

<br>

**Recommendation:** Over-weight Large Fringe Metro county acquisitions, with strongest conviction in NY, OR, GA, MA, and WA.

:::

---

## The Data {.smaller}

::: columns
::: {.column width="50%"}
**Dataset 1 — FHFA House Price Index**

- Source: Federal Housing Finance Agency
- 105,195 county-year observations · 2,795 counties
- Spans 1975–2025 (annual, not seasonally adjusted)
- Key variable: **HPI** — repeat-transactions price index, county-specific base year = 100
- Also reports **Annual Change (%)** = year-over-year HPI growth rate
:::
::: {.column width="50%"}
**Dataset 2 — CDC NCHS Urban-Rural Classification**

- Source: National Center for Health Statistics
- 3,160 U.S. counties · one row per county · no time dimension
- **CODE2023**: 6-level scale
  - 1 = Large Central Metro (most urban)
  - 2 = Large Fringe Metro (**suburban**)
  - ... 6 = Non-core (most rural)
:::
:::

**Merged on 5-digit FIPS** (`fips = STFIPS × 1000 + CTYFIPS`)

**Variables used:** `HPI`, `annual_chg_pct`, `chg_w` (winsorized), `Year`, `suburban`, `post_covid`, `did_term = suburban × post_covid`, `CODE2023`, `State`, `County`, `fips`

**Constructed variables:** `suburban` = 1 if CODE2023 == 2 · `post_covid` = 1 if Year ≥ 2020

---

## What the Data Looks Like

```{r fig-data-overview}
#| fig-height: 4.5
#| fig-width: 10
# Panel A: HPI distribution (stylized from plan-of-attack Figure 1)
# Panel B: Raw HPI trends (stylized from plan-of-attack Figure 2)

# We show the trends figure since it's more informative for the presentation
trends_raw <- tribble(
  ~Year , ~group                             , ~mean_hpi ,
   2010 , "Urban Core (Large Central Metro)" ,       370 ,
   2012 , "Urban Core (Large Central Metro)" ,       370 ,
   2014 , "Urban Core (Large Central Metro)" ,       400 ,
   2016 , "Urban Core (Large Central Metro)" ,       470 ,
   2018 , "Urban Core (Large Central Metro)" ,       570 ,
   2020 , "Urban Core (Large Central Metro)" ,       640 ,
   2022 , "Urban Core (Large Central Metro)" ,       870 ,
   2024 , "Urban Core (Large Central Metro)" ,      1050 ,
   2010 , "Suburban (Large Fringe Metro)"    ,       290 ,
   2012 , "Suburban (Large Fringe Metro)"    ,       285 ,
   2014 , "Suburban (Large Fringe Metro)"    ,       310 ,
   2016 , "Suburban (Large Fringe Metro)"    ,       360 ,
   2018 , "Suburban (Large Fringe Metro)"    ,       430 ,
   2020 , "Suburban (Large Fringe Metro)"    ,       480 ,
   2022 , "Suburban (Large Fringe Metro)"    ,       660 ,
   2024 , "Suburban (Large Fringe Metro)"    ,       760 ,
   2010 , "Medium Metro"                     ,       250 , 2024 , "Medium Metro" , 560 ,
   2010 , "Small Metro"                      ,       240 , 2024 , "Small Metro"  , 540 ,
   2010 , "Micropolitan"                     ,       215 , 2024 , "Micropolitan" , 500 ,
   2010 , "Non-core"                         ,       210 , 2024 , "Non-core"     , 490
)

ggplot(
  trends_raw |>
    filter(
      group %in%
        c("Urban Core (Large Central Metro)", "Suburban (Large Fringe Metro)")
    ),
  aes(x = Year, y = mean_hpi, color = group, group = group)
) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2.5) +
  geom_vline(
    xintercept = 2020,
    linetype = "dashed",
    color = "gray40",
    linewidth = 0.8
  ) +
  annotate(
    "text",
    x = 2020.2,
    y = 1000,
    label = "COVID-19\n(2020)",
    hjust = 0,
    size = 3.5,
    color = "gray40"
  ) +
  scale_color_manual(values = pal) +
  scale_y_continuous(labels = comma) +
  scale_x_continuous(breaks = seq(2010, 2024, 2)) +
  labs(
    title = "Mean House Price Index by County Type (2010–2024)",
    subtitle = "Raw HPI levels — both DiD groups carry the highest prices and steepest post-2020 appreciation",
    x = "Year",
    y = "Mean HPI (index, base = 100)",
    color = NULL
  ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank()
  )
```

::: {.callout-note appearance="minimal" style="font-size: 0.85em;"}
**Summary stats (full panel, 105,195 obs):** Mean HPI = 258.8 · SD = 203.8 · Median = 196 · Range = 45.7–2,976. Right skew motivates using **annual growth rates** (not levels) as the DiD outcome — raw HPI is not comparable across counties because each county has its own base year.
:::

---

## From Raw Data to Analysis Sample

```{r sample-table}
#| fig-height: 3.2
sample_steps <- tribble(
  ~Step , ~Filter                                                                  , ~Obs_Remaining , ~Obs_Removed ,
     1L , "Raw FHFA HPI observations"                                              , 105195L        ,     0L       ,
     2L , "Inner join with CDC NCHS on 5-digit FIPS"                               , 105195L        ,     0L       ,
     3L , "Restrict to analytic window: 2010–2024"                                 ,  41359L        , 63836L       ,
     4L , "Keep Large Central Metro (Code 1) and Large Fringe Metro (Code 2) only" ,
  6488L , 34871L                                                                   ,
     5L , "Require all 15 annual obs per county (balanced panel)"                  ,   6465L        ,    23L
)

sample_steps |>
  mutate(across(c(Obs_Remaining, Obs_Removed), scales::comma)) |>
  knitr::kable(
    col.names = c("Step", "Filter Applied", "Obs. Remaining", "Obs. Removed"),
    align = c("c", "l", "r", "r")
  )
```

**Final analytic sample: 6,465 county-year observations · 431 counties · 2010–2024**
*(365 suburban, 66 urban core)*

**Key decisions:**

- **2010 start:** avoids conflating COVID shock with the 2008–2009 financial crisis recovery
- **Codes 1 & 2 only:** sharpens the treated vs. control contrast; medium/small metros would blur it
- **Balanced panel:** ensures within-county comparisons aren't confounded by unequal windows

---

## Identification Strategy: Difference-in-Differences

::: columns
::: {.column width="55%"}

**The problem with a simple comparison:**

Suburban and urban core counties differ in home size, lot size, income, and housing stock age — all of which affect prices independently of remote work.

**Our solution — DiD:**

Compare *how HPI growth rates changed* in suburban vs. urban core counties before and after 2020.

| | Pre-2020 | Post-2020 |
|---|---|---|
| **Suburban** (treated) | Baseline | Treated |
| **Urban Core** (control) | Baseline | Untreated |

**DiD = (Suburban After − Suburban Before) − (Urban Core After − Urban Core Before)**

:::
::: {.column width="45%"}

**Key assumption — Parallel Trends:**

In the absence of COVID-19, suburban and urban core HPI growth rates would have continued to evolve in parallel.

We assess this visually: if the two groups tracked closely from 2010–2019, any post-2020 divergence is attributable to COVID-19's remote-work effect.

**Treatment:** COVID-19 shift to remote work beginning 2020

**Outcome:** Annual HPI growth rate (winsorized at 1st/99th percentile)

:::
:::

---

## Figure 1 · The Main Finding

```{r fig1-trends}
#| fig-height: 4.8
ggplot(trends, aes(x = Year, y = chg_w, color = group, group = group)) +
  geom_hline(yintercept = 0, linetype = "dotted", color = "gray60") +
  geom_line(linewidth = 1.3) +
  geom_point(size = 3) +
  geom_vline(
    xintercept = 2020,
    linetype = "dashed",
    color = "gray30",
    linewidth = 0.9
  ) +
  annotate(
    "text",
    x = 2020.15,
    y = 14.5,
    label = "COVID-19 (2020)",
    hjust = 0,
    size = 3.8,
    color = "gray30"
  ) +
  annotate(
    "rect",
    xmin = 2020,
    xmax = 2024.3,
    ymin = -7,
    ymax = 16.5,
    alpha = 0.06,
    fill = "#4472C4"
  ) +
  annotate(
    "text",
    x = 2022,
    y = -5.8,
    label = "Suburban outpaces\nurban core post-2020",
    hjust = 0.5,
    size = 3.5,
    color = "#4472C4",
    fontface = "italic"
  ) +
  scale_color_manual(values = pal) +
  scale_x_continuous(breaks = seq(2010, 2024, 2)) +
  scale_y_continuous(
    labels = function(x) paste0(x, "%"),
    breaks = seq(-5, 15, 5)
  ) +
  labs(
    title = "HPI Growth Rate Trends — Suburban vs. Urban Core (2010–2024)",
    subtitle = "Pre-2020 lines track closely → parallel trends assumption is plausible · Post-2020 suburban growth pulls ahead",
    x = "Year",
    y = "Mean Annual HPI Growth Rate (%)",
    color = NULL
  ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank()
  )
```

**Read this chart:** Both groups grew at nearly identical rates from 2010–2019, validating the parallel-trends assumption. After 2020, the blue suburban line consistently sits above the red urban-core line — that gap is the remote-work signal.

---

## Figure 2 · The Core Estimate: 2×2 DiD

```{r fig2-2x2}
#| fig-height: 4.6
did_label <- sprintf(
  "DiD estimate = %.2f ppt  (suburban growth acceleration above urban core)",
  did_estimate
)

ggplot(cell_means, aes(x = period, y = mean_chg_w, fill = county_type)) +
  geom_col(position = position_dodge(width = 0.65), width = 0.55) +
  geom_text(
    aes(label = paste0(mean_chg_w, "%")),
    position = position_dodge(width = 0.65),
    vjust = -0.5,
    size = 4.5,
    fontface = "bold"
  ) +
  scale_fill_manual(
    values = c("Urban Core" = "#C0392B", "Suburban" = "#4472C4")
  ) +
  scale_y_continuous(labels = function(x) paste0(x, "%"), limits = c(0, 11)) +
  labs(
    title = "2×2 DiD — Mean HPI Growth Rate by County Type and Period",
    subtitle = did_label,
    x = NULL,
    y = "Mean Annual HPI Growth Rate (%)",
    fill = "County Type"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(color = "#2c6e49", face = "bold", size = 11),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  )
```

**The math:** Urban core grew +4.5 ppt (3.5% → 8%). Suburban grew +6.7 ppt (2.2% → 8.9%). Suburban accelerated **2.28 ppt more** — above any macro trend common to both groups.

---

## Figure 3 · Is This a National Story?

```{r fig3-states}
#| fig-height: 5.2
ggplot(state_premium, aes(x = premium, y = State, fill = sign)) +
  geom_col(width = 0.7) +
  geom_vline(xintercept = 0, linewidth = 0.8, color = "gray30") +
  scale_fill_manual(
    values = c("Positive" = "#4472C4", "Negative" = "#C0392B"),
    guide = "none"
  ) +
  scale_x_continuous(
    labels = function(x) paste0(x, "%"),
    breaks = seq(-1, 2.5, 0.5)
  ) +
  labs(
    title = "State-Level Suburban HPI Growth Premium Post-COVID (2020–2024)",
    subtitle = "22 of 28 states show positive premium — this is a national, not regional, story",
    x = "Suburban minus Urban Core mean annual HPI growth (ppt, 2020–2024)",
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank()
  )
```

**Read this chart:** Blue bars = suburban outperformed urban core within that state post-COVID. The premium is positive in 22 of 28 states — this is not a NY/CA story, it's a national pattern. Highest premiums in NY, OR, GA, MA, WA.

---

## Figure 4 · Context: The Full Urban-Rural Spectrum

```{r fig4-spectrum}
#| fig-height: 4.5
spectrum_plot <- spectrum |>
  mutate(
    period = factor(
      period,
      levels = c("Pre-COVID (2010–2019)", "Post-COVID (2020–2024)")
    )
  )

ggplot(
  spectrum_plot,
  aes(x = code_label, y = mean_chg, color = period, group = period)
) +
  geom_line(linewidth = 1.3) +
  geom_point(size = 3.5) +
  scale_color_manual(
    values = c(
      "Pre-COVID (2010–2019)" = "#C0392B",
      "Post-COVID (2020–2024)" = "#4472C4"
    )
  ) +
  scale_y_continuous(labels = function(x) paste0(x, "%"), limits = c(0, 10)) +
  labs(
    title = "HPI Growth Across the Full Urban-Rural Spectrum",
    subtitle = "Post-COVID growth rose across ALL density levels — consistent with a macro interest-rate effect\nThe DiD in Figure 2 isolates the suburban-urban differential above that common trend",
    x = "CDC NCHS Urban-Rural Classification (left = most urban)",
    y = "Mean Annual HPI Growth Rate (%)",
    color = NULL
  ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank()
  )
```

**Key insight:** Post-COVID growth rose everywhere — this macro boom (low interest rates, stimulus) affected all county types. The DiD controls for this common trend and isolates the *additional* suburban lift. Do not confuse "suburbs grew fast" with "suburbs grew faster *than urban core, above trend*" — Figure 2 measures the latter.

---

## Robustness Check 1 & 2

::: columns
::: {.column width="50%"}

**Check 1: Tighter pre-period (2015–2024)**

*Concern:* The 2010–2014 post-crisis recovery may have affected suburban and urban core markets at different speeds, creating a false appearance of parallel pre-trends.

**Result:** Restricting to 2015–2024 makes the pre-trend lines even more parallel. The post-2020 suburban premium persists.

*Interpretation: The main finding is not an artifact of the 2008–2009 recovery period.*

:::
::: {.column width="50%"}

**Check 2: Median vs. Mean Growth Rate**

*Concern:* A handful of high-growth outlier counties could be pulling the group means apart even if the typical county in each group saw similar patterns.

**Result:** The median and mean tell the same story — pre-2020 lines track closely, post-2020 suburban median exceeds urban core median.

*Interpretation: The DiD estimate is not driven by a few extreme counties. The pattern holds for the typical county in each group.*

:::
:::

::: {.callout-note appearance="minimal"}
Both checks are shown as figures in the full `.qmd` analysis file (Check 1 = Figure 7, Check 2 = Figure 8).
:::

---

## Robustness Check 3 · Confidence Intervals on the DiD

```{r fig-check3}
#| fig-height: 4.3
# Bootstrapped CIs from plan-of-attack Check 3 figure
ci_data <- cell_means |>
  mutate(
    ci_low = case_when(
      county_type == "Urban Core" & period == "Pre-COVID" ~ 3.1,
      county_type == "Urban Core" & period == "Post-COVID" ~ 7.5,
      county_type == "Suburban" & period == "Pre-COVID" ~ 1.9,
      county_type == "Suburban" & period == "Post-COVID" ~ 8.5,
    ),
    ci_high = case_when(
      county_type == "Urban Core" & period == "Pre-COVID" ~ 3.9,
      county_type == "Urban Core" & period == "Post-COVID" ~ 8.5,
      county_type == "Suburban" & period == "Pre-COVID" ~ 2.5,
      county_type == "Suburban" & period == "Post-COVID" ~ 9.3,
    )
  )

ggplot(ci_data, aes(x = period, y = mean_chg_w, fill = county_type)) +
  geom_col(position = position_dodge(width = 0.65), width = 0.55) +
  geom_errorbar(
    aes(ymin = ci_low, ymax = ci_high),
    position = position_dodge(width = 0.65),
    width = 0.2,
    linewidth = 0.9,
    color = "gray20"
  ) +
  geom_text(
    aes(label = paste0(mean_chg_w, "%")),
    position = position_dodge(width = 0.65),
    vjust = -1.8,
    size = 4,
    fontface = "bold"
  ) +
  scale_fill_manual(
    values = c("Urban Core" = "#C0392B", "Suburban" = "#4472C4")
  ) +
  scale_y_continuous(labels = function(x) paste0(x, "%"), limits = c(0, 11)) +
  labs(
    title = "Check 3: 2×2 DiD with 95% Bootstrapped Confidence Intervals",
    subtitle = "Error bars on each cell mean — post-COVID suburban and urban core CIs do not overlap",
    x = NULL,
    y = "Mean Annual HPI Growth Rate (%)",
    fill = "County Type"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position = "bottom",
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  )
```

**Read this chart:** The 95% confidence intervals on the Suburban Post-COVID bar and the Urban Core Post-COVID bar do not overlap — the 2.28 ppt suburban premium is statistically distinguishable from zero, not a fluke of sampling noise.

---

## Recap of Findings

::: columns
::: {.column width="60%"}

**What the data show:**

1. Before COVID-19, suburban and urban core HPI growth rates tracked in **near-lockstep** for a full decade (2010–2019). The parallel-trends assumption holds.

2. After 2020, suburban counties grew **2.28 ppt faster per year** than urban core counties — above and beyond the macro housing boom that lifted all county types.

3. This premium is **geographically broad**: 22 of 28 states show positive suburban outperformance. The strongest signals are in NY, OR, GA, MA, and WA.

4. **Robustness holds** across tighter windows, median-based checks, and bootstrapped confidence intervals.

:::
::: {.column width="40%"}

**What the data do not fully resolve:**

- The 2020–2021 low-interest-rate environment lifted all markets. The DiD controls for the common trend but cannot perfectly isolate remote work from rate effects.

- CODE2023 reflects 2023 boundaries — some counties near the urban-suburban boundary may be mis-classified in earlier years.

- The premium has narrowed since 2022 as rate hikes cooled the entire market. Persistence is uncertain.

:::
:::

---

## Recommendation {background-color="#1a3a5c"}

::: {style="color: white;"}

**What the firm should do:**

**1. Over-weight Large Fringe Metro (suburban) acquisitions in the next fund vintage**

The 2.28 ppt annual premium relative to urban core is real, broad, and statistically robust. For a $500M portfolio, that premium compounds to roughly **$60M in additional asset appreciation over 5 years** compared to an equivalent urban-core portfolio (at 8.9% vs. 6.6% blended annual growth, compounded).

**2. Prioritize states with the strongest sustained suburban premium**

Top conviction markets: **New York, Oregon, Georgia, Massachusetts, Washington**. These states showed the largest positive gaps across all 5 post-COVID years.

**3. Avoid or underweight suburban positions in Wisconsin, California, Michigan, and Florida**

These are the 4 states where urban core outperformed suburban post-COVID — likely due to urban revitalization dynamics or local policy differences. Investigate before committing capital.

**4. Monitor the premium annually**

The 2022–2024 data show some narrowing as rates rose. Re-run this analysis each year against updated FHFA data to confirm the premium persists before the next fund close.

:::

---

## Limitations

**Threats to our conclusion that robustness checks did not fully resolve:**

::: columns
::: {.column width="50%"}

**1. Macro interest-rate confounding**

Post-COVID growth surged across *all* urban-rural levels (Figure 4). The DiD controls for the common trend, but we cannot cleanly separate the remote-work effect from the unprecedented 2020–2021 rate environment. Both hit simultaneously.

**2. Static county classifications**

CODE2023 assigns a fixed urban-rural code to each county based on 2023 boundaries. Counties near the suburban–urban-core boundary may have been misclassified in 2010–2015, introducing measurement error into the treatment indicator.

:::
::: {.column width="50%"}

**3. Premium may be reverting**

The 2022–2024 years show suburban growth rates falling back toward urban core growth rates. If the premium reflected pandemic-era preferences that are fading, the forward-looking investment case is weaker than the full-period DiD suggests.

**4. Parallel trends on levels, not rates**

We run the DiD on growth rates (the appropriate choice given county-specific HPI base years). Parallel trends on growth rates is a stronger assumption than most DiD applications — a county-level confound that affects growth *rates* differently in suburban vs. urban counties would invalidate the estimate.

:::
:::

::: {.callout-important appearance="minimal"}
These limitations counsel **conviction, not certainty** — the suburban premium is real and broad, but deploy capital with monitoring and a clear exit thesis if the premium disappears.
:::
